Galois Transformers and Modular Abstract Interpreters

### 2015-03-23 writeup/oopsla2015.tex
Finally figured out flow sens.
So, flow sensitivity was wrong in the initial paper, and then I fixed it
and it was subtly wrong again. I finally fixed it so that flow
sensitivity accurately represents "one set of facts per program point".

The issue now is the examples. Flow sensitivity is only helpful if the
facts at one program point are different in an interesting way than from
another program point. In imperative languages this happens through
strong update. In our little functional language, information (the
store) is growing strictly monotonically. This means that a
flow-insensitive and

\documentclass[10pt,preprint]{sigplanconf}

@@

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\usepackage{balance}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[font=small,skip=0pt]{caption}
% \usepackage[belowskip=-15pt,aboveskip=0pt]{caption}

@@

\newcommand\litM{M}
\newcommand\litTime{Time}
\newcommand\litStore{Store}
\newcommand\litVal{Val}
\newcommand\litKAddr{KAddr}
\newcommand\litKStore{KStore}
\newcommand\litEnv{Env}
\newcommand\litClo{Clo}

\newcommand{\itop}[1]{\operatorname{\mathit{#1}}}
\newcommand{\ttbfop}[1]{\operatorname{\mathtt{\boldsymbol{\mathbf{#1}}}}}
\newcommand{\ttbfbin}[1]{\mathbin{\mathtt{\mathbf{\boldsymbol{#1}}}}}
\newcommand{\ttop}[1]{\operatorname{\mathtt{#1}}}
\newcommand{\Concrete}[1]{\mathtt{\mathbf{#1}}}
\newcommand{\Abstract}[1]{\widehat{\mathtt{\mathbf{#1}}}}

@@

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

@@

% These are supposed to make align* not have breaks around it...
% \setlength{\abovedisplayskip}{0em}
% \setlength{\belowdisplayskip}{0em}
% \setlength{\abovedisplayshortskip}{0em}
% \setlength{\belowdisplayshortskip}{0em}

\title{Galois Transformers and Modular Abstract Interpreters}
\subtitle{Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{University of Maryland, USA}{darais@cs.umd.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

@@

The design and implementation of static analyzers have becoming increasingly
systematic.  In fact, for large classes of analyzers, design and implementation
have remained seemingly (and now stubbornly) on the verge of full mechanization
for several years.  A stumbling block in full mechanization has been the
\emph{ad hoc} nature of soundness proofs accompanying each analyzer. While
design and implementation is largely systematic, soundness proofs can change
significantly with seemingly minor changes to the semantics or analyzers.  An
achievement of this work is to systematize, parameterize and modularize the
proofs of soundness, so as to make them composable across analytic properties.

@@

\category{CR-number}{subcategory}{third-level}
\terms term1, term2
\keywords keyword1, keyword2

\input{tmp/autogen/pldi15.markdown.tex}

\appendix
\section{Appendix Title}

Appendix body.

\acks

Acknowledgments body.

>>>>

\documentclass[nocopyrightspace,preprint,10pt]{sigplanconf}

@@

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\usepackage{balance}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[font=small,skip=0pt]{caption}

@@

\newcommand\litM{M}
\newcommand\litTime{Time}
\newcommand\litStore{Store}
\newcommand\litVal{Val}
\newcommand\litKAddr{KAddr}
\newcommand\litKStore{KStore}
\newcommand\litEnv{Env}
\newcommand\litClo{Clo}
\newcommand\litelse{else}

\newcommand{\itop}[1]{\operatorname{\mathit{#1}}}
\newcommand{\ttop}[1]{\operatorname{\mathtt{#1}}}
\newcommand{\ttbfop}[1]{\ttop{\boldsymbol{\mathbf{#1}}}}
\newcommand{\ttbfbin}[1]{\mathbin{\mathtt{\mathbf{\boldsymbol{#1}}}}}
\newcommand{\keyword}[1]{\underline{\ttbfop{#1}}}
\newcommand{\keywordop}[1]{\ttbfbin{#1}}
\newcommand{\Concrete}[1]{\mathtt{\mathbf{#1}}}
\newcommand{\Abstract}[1]{\widehat{\mathtt{\mathbf{#1}}}}

@@

% \conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
% \copyrightyear{20yy} 
% \copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

@@

% These are supposed to make align* not have breaks around it...
\setlength{\abovedisplayskip}{0em}
\setlength{\belowdisplayskip}{0em}
\setlength{\abovedisplayshortskip}{0em}
\setlength{\belowdisplayshortskip}{0em}

\title{Galois Transformers and Modular Abstract Interpreters}
\subtitle{Reusable Metatheory for Program Analysis}
% \authorinfo{David Darais}{University of Maryland, USA}{darais@cs.umd.edu}
% \authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
% \authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\authorinfo{}{}{}
\maketitle

@@

The design and implementation of static analyzers have becoming
increasingly systematic.  Yet for a given language or analysis
feature, it often requires tedious and error prone work to implement
an analyzer and prove it sound.
%
In short, static analysis features and their proofs of soundness do
not compose well, causing a dearth of reuse in both implementation and
metatheory.

@@

% \category{CR-number}{subcategory}{third-level}
% \terms term1, term2
% \keywords keyword1, keyword2

\input{tmp/autogen/paper.markdown.tex}

% \appendix
% \section{Appendix Title}
% 
% Appendix body.
% 
% \acks
% 
% Acknowledgments body.
